### 2013-11-18 proposal/proposal/chapter1.tex
chnages

\section{Motivations and research questions}\label{sec:motivation}

@@

Most of the recent work on communities of services are either
user-centric and focus on user satisfaction
\cite{Chun02user-centricperformance} or system-centric and focus
on the whole system throughput, performance and utilization. There
are many contributions in distributed, grid, cluster and cloud
services which are system-centric. However, in real world
environments and applications, both users and service providers
are self-interested agents, aiming to maximize their own profit.
In those environments, both parties (users and services) will
collaborate as long as they are getting more benefits and payoff.

In this direction, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed mechanisms to help
users and services to maximize their gain. A two-player
non-cooperative game between web services and community master was
introduced in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. In this
game-theoretic model, the strategies available to a web service
when facing a new community are requesting to join the community,
accepting the master's invitation to join the community, or
refusing the invitation to join. The set of strategies for
communities are inviting the web service or refusing the web
service's join request. Based on their capacity, market share and
reputation, the two players have different set of utilities over
the strategy profiles of the game. The main limits of this game
model are: 1) its consideration of only three quality parameters,
while the other factors are simply ignored; and 2) the
non-consideration of the web services already residing within the
community. The game is only between the community master and the
new web service, and the inputs from all the other members are
simply ignored. The consideration of those inputs is a significant
issue as existing web services can lose utility or payoff because
of the new member, which can results in an unhealthy and unstable
group. The problem comes from the fact that the existing members
should collaborate with the new web services, so probably their
performance as a group can suffer. Existing members may even
deviate and try to join other communities if they are unsatisfied.
Those considerations of forming stable and efficient coalitions
are the main contributions of our paper.

In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
for selecting web services has been proposed. In this approach,
the authors proposed a web service selection process that the
community masters can use. The approach considers the efficiency
of all the three involved parties, namely users, web services and
communities. In this work, it is shown how the gains of these
parties are coupled together using a linear optimization process.
However, the optimization problem in this solution tends to
optimize some parameters considering all web services regardless
of their efficiency and contribution to the community's welfare.
Moreover, there are no clear thresholds for accepting or rejecting
new web services. The solution of the optimization problem could,
for instance, suggest web services already residing within the
community to increase or decrease their capacity to cover up the
weakness of other parties in the system. However, a high
performing web service could deviate anytime it finds itself
unsatisfied within the community instead of adjusting its service
parameters.

@@

\section{Research objectives and contributions}\label{sec:contribution}

In this research work, we use game theory to
propose a cooperative game model for the aggregation of web
services within communities. The solution concepts of our
cooperative game seeks to find efficient ways of forming
coalitions (teams) of web services so that they can maximize their
gain and payoff, and distribute the gain in a fair way among all
the web services. Achieving Fairness when the gain is distributed
among the community members is the main factor to keep the
coalition stable as no web service will expect to gain better by
deviating for the community. In other words, the coalition is made
efficient if all the members are satisfied. We first propose a
representation function for communities of web services based on
their QoS attributes. By using this function, we can evaluate the
$worth$ of each community of web services. When facing new
membership requests, a typical community master checks whether the
new coalition having the old and new set of web services will keep
the community stable or not. The community master will reject the
membership requests if it finds out that the new coalition would
be unstable, preventing $any$ subset of web services from gaining
significantly more by deviating from the community and joining
other communities or forming new ones. The computation of
solutions for cooperative game theory problems is combinatorial in
nature and proven to be NP-complete \cite{Algorithmic}, making
this computation impractical in real world applications. However,
using the concepts of coalition stability, we propose
approximation algorithms running in polynomial time providing web
services and community masters with applicable and near-optimal
decision making mechanisms.

\section{Research outline}\label{sec:outline}
The rest of the paper is organized as follows: We present in Chapter~\ref{sec:MAS} the background
needed for our research along with the relevant related work. Chapter 3 provides the problem statement and presents our solution model in two
different scenarios with some primitive results. Finally in Chapter 4, we present our conclusion, future plan, and the timetable of our research.

>>>>

\section{Context}\label{sec:motivation}

@@

@@

\section{Motivation and research Questions}\label{sec:researchquestions}

Web service communities are dynamic by design \cite{DBLP:journals/ijebr/MaamarSTBB09}. Web services are modeled as intelligent autonomous agents, where they can adopt a strategy maximizing their payoff at any time. In web service communities, a web service has its own right to determine when to join a community and when to leave a community. Community managers can invite or ask a web service to leave in order to maximise their profit. Users can simply stop sending requests to a web service which is not providing satisfactory services.

Most of the recent work on communities of services are either
user-centric and focus on user satisfaction
\cite{Chun02user-centricperformance} or system-centric and focus
on the whole system throughput, performance and utilization. There
are many contributions in distributed, grid, cluster and cloud
services which are system-centric. However, in real world
environments and applications, both users and service providers
are self-interested agents, aiming to maximize their own profit.
In those environments, both parties (users and services) will
collaborate as long as they are getting more benefits and payoff. 
Our initial research question is:
\emph{How can we model the community of services for the autonomous agents, in order to maximize the throughput for users, web services and community organizers involved?}

In order to address this shortcoming, recently \cite{DBLP:conf/IEEEscc/LimTMB12,
DBLP:conf/IEEEscc/KhosravifarABT11, 10.1109/TSC.2012.12} proposed mechanisms to help
users and services to maximize their gain. A two-player
non-cooperative game between web services and community master was
introduced in \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. 
In \cite{DBLP:conf/IEEEscc/LimTMB12}, a 3-way satisfaction approach
for selecting web services has been proposed. In this approach,
the authors proposed a web service selection process that the
community masters can use. The approach considers the efficiency
of all the three involved parties, namely users, web services and
communities.

%The consideration of those inputs is a significant
%issue as existing web services can lose utility or payoff because
%of the new member, which can results in an unhealthy and unstable
%group. The problem comes from the fact that the existing members
%should collaborate with the new web services, so probably their
%performance as a group can suffer. Existing members may even
%deviate and try to join other communities if they are unsatisfied.
%Those considerations of forming stable and efficient coalitions
%are the main contributions of our paper.

%However, a high
%performing web service could deviate anytime it finds itself
%unsatisfied within the community instead of adjusting its service
%parameters.

Our question we would like to explore is:
\emph{How can we model the the fairness efficiently in communities of web services and form stable communities?}

Another research question we would like to work on is:
\emph{How can we model the community of web services based on cooperative game theory models in a realistic and applicable way?}

\section{Research Objectives and contributions}\label{sec:motexample}

In this research work, I will use game theory to
propose a cooperative game model for the aggregation of web
services within communities. The solution concepts of our
cooperative game seeks to find efficient ways of forming
coalitions (teams) of web services so that they can maximize their
gain and payoff, and distribute the gain in a fair way among all
the web services. Achieving Fairness when the gain is distributed
among the community members is the main factor to keep the
coalition stable as no web service will expect to gain better by
deviating for the community. In other words, the coalition is made
efficient if all the members are satisfied. We first propose a
representation function for communities of web services based on
their QoS attributes. By using this function, we can evaluate the
$worth$ of each community of web services. When facing new
membership requests, a typical community master checks whether the
new coalition having the old and new set of web services will keep
the community stable or not. The community master will reject the
membership requests if it finds out that the new coalition would
be unstable, preventing $any$ subset of web services from gaining
significantly more by deviating from the community and joining
other communities or forming new ones. The computation of
solutions for cooperative game theory problems is combinatorial in
nature and proven to be NP-complete \cite{Algorithmic}, making
this computation impractical in real world applications. However,
using the concepts of coalition stability, we propose
approximation algorithms running in polynomial time providing web
services and community masters with applicable and near-optimal
decision making mechanisms.

\indent In this proposal, I will address the problem of forming stable and efficient coalitions for maximising web services and community revenue.
The main objectives in this proposal work are:
\begin{itemize}
\item To apply cooperative game theory solution concepts in order to address the problem of optimizing coalition formation for a stable community that can maximise the total payoff.
\item To reduce the complexity of cooperative game theory solution concepts tailored to the problem model of communities of web services in order to make these solutions applicable in real world scenarios.
\item To increase community stability by subsiding and taxation methods.
\item To validate the proposed methods by simulation and comparing our results with other similar works.
\end{itemize}

\section{Proposal Organization}\label{sec:outline}
The rest of the paper is organized as follows: We present in Chapter~\ref{sec:MAS} the background
needed for our research along with the relevant related work. Chapter~\ref{sec:coalitionformationws} provides the problem statement and presents our solution model in two
different scenarios with some primitive results. Finally in Chapter 4, we present our conclusion, future plan, and the timetable of our research.
